Draft: Information, Ideology, and Anti-Vaccination Attitudes

### 2019-04-02 paper-template.Rmd
Need to link references to zotero

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms2.tex
title: "Information, Ideology, and Anti-Vaccination Attitudes" 
thanks: "The paper's revision history and the materials needed to reproduce its analyses can be found [on Github here](https://github.com/aq92/7450paper.git). Corresponding author: [ahmad-qbazard@uiowa.edu](mailto:ahmad-qabazard@uiowa.edu). Current version: `r format(Sys.time(), '%B %d, %Y')`."
author:
- name: Ahmad S. Qabazard
  affiliation: University of Iowa
abstract: "Anti-vaccination attitudes are prevalent among individuals affiliated with both major political parties. What determines anti-vaccination attitudes? Using survey responses of 1,000 US adults, I find that individual and state level variables contribute to attitudes towards vaccination. Using data from a 2015 telephone survey, I identify anti-vaccination attitudes using item response models. I show the presence of anti-vaccination attitudes among respondents by looking at responses to survey questions using graded response and nominal response models. I find that respondents from states with higher insured citizens are less likely to have skeptical attitudes towards vaccinations. I established the necessity of looking at vaccinations as latent constructs by showing the difference in model predictions. Using a mixed linear model, I predict values of a latent construct, theta, and the results show relationships that are obscured by looking at direct responses with a multinomial logit."
keywords: "Vaccination, State Politics"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 12pt
spacing: single
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), "bib$"))`}
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
---

@@

## Other Common Things

> This will create a block quote, if you want one.
Dropping a footnote is easy.^[See? Not hard at all.]

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms2.tex
title: "Draft: Information, Ideology, and Anti-Vaccination Attitudes" 
thanks: "The paper's revision history and the materials needed to reproduce its analyses can be found [on Github here](https://github.com/aq92/7450paper.git). Corresponding author: [ahmad-qbazard@uiowa.edu](mailto:ahmad-qabazard@uiowa.edu). Current version: `r format(Sys.time(), '%B %d, %Y')`."
author:
- name: Ahmad S. Qabazard
  affiliation: University of Iowa
abstract: "Anti-vaccination attitudes are prevalent among individuals affiliated with both major political parties. What determines anti-vaccination attitudes? Using survey responses of 1,000 US adults, I find that individual and state level variables contribute to attitudes towards vaccination. Using data from a 2015 telephone survey, I identify anti-vaccination attitudes using item response models. I show the presence of anti-vaccination attitudes among respondents by looking at responses to survey questions using graded response and nominal response models. I find that respondents from states with higher insured citizens are less likely to have skeptical attitudes towards vaccinations. I established the necessity of looking at vaccinations as latent constructs by showing the difference in model predictions. Using a mixed linear model, I predict values of a latent construct, theta, and the results show relationships that are obscured by looking at direct responses with a multinomial logit."
keywords: "Vaccination, State Politics"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 12pt
spacing: single
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), "bib$"))`}
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
---

@@
